%\documentclass[12pt]{article}
\documentclass[aps,rmp]{revtex4}

\usepackage{times}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
\usepackage{hyperref}
%\usepackage{natbib}
\newcommand{\bm}[1]{\mbox{\boldmath $#1$}}
\newcommand{\EQ}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\EQS}[2]{Eqs.~(\ref{eq:#1)} and (\ref{eq:#2})}
\newcommand{\FIG}[1]{Fig.~\ref{fig:#1}}
\newcommand{\TAB}[1]{Tab.~\ref{tab:#1}}
\newcommand{\REF}[1]{ref.~\cite{#1}}


\begin{document}
\title{Ligation barcoding: step by step}

\maketitle

For DNA obtained from the University Hospital Basel, start with A-tailing. Their concentration measurements can be be trusted. Fragmentation, end-repair, bead-clean up and qubit can be skipped.

\section*{Prepare}
\begin{itemize}
	\item 70\% Ethanol needed for bead clean-up: $4n\times 200\mu l$ + some extra. prepare fresh.
	\item Qubit solution: at least $2n+5$ reactions ($200\mu l $ each)
	\item Switch on heat block
	\item Get aliquot of NFW if not at bench.
	\item Get bucket of ice.
\end{itemize}

\section*{A-tailing}
\begin{itemize}
	\item Required for each sample: 1000ng DNA in 50$\mu l$ nuclease free water
	\item Add: $7\mu l$ Ultra II End-prep buffer	(green cap)
	\item Add: $3\mu l$ Ultra II End-prep enzyme mix (green cap)
	\item mix by inversion (or gentle pipetting), spin down
	\item 5min at RT
	\item 5min at 65C (heat block can be switched off now)
\end{itemize}

\section*{Clean-up}
{\bf resuspend the beads by vortexing. use an aliquot at RT}.
\begin{itemize}
	\item Add $60\mu l$ of beads
	\item mix and incubate 5min on rotator. briefly spin to collect any droplets from lid
	\item pellet on magnet, remove supernatant
	\item add $200\mu l$ of 70\% ethanol. keep on magnet, don't resuspend.
	\item remove ethanol, repeat ethanol wash.
	\item spin down, remove residual wash, let pellet air-dry (a few minutes)
	\item label new set of tubes.
	\item add $25\mu l$ NFW, resuspend pellet, incubate 2min
	\item transfer eluate to fresh tube.
	\item use $1\mu l$ for qubit. (aim 700ng, 500ng more typical)
\end{itemize}

\section*{Barcode ligation}
{\bf Thaw the barcodes. I sometimes thaw them by turning them up-side down and filling the hollow tube with (cold) water. Add barcodes to sample sheet}.
\begin{itemize}
	\item dilute DNA to 500ng/$22\mu l$. Or just use of all of it if within 400-600ng
	\item add $2.5\mu l$ barcode
	\item add $25\mu l$ TA ligase
	\item mix by inversion, spin down, incubate at RT for 10 min
\end{itemize}

\section*{Clean up}
{\bf  Note: pellet is typically diffuse at this step}
\begin{itemize}
	\item Add $60\mu l$ of AmpXP beads
	\item mix and incubate 5min on rotator. briefly spin to collect any droplets from lid
	\item pellet on magnet, remove supernatant
	\item add $200\mu l$ of 70\% ethanol. keep on magnet, don't resuspend.
	\item remove ethanol, repeat ethanol wash.
	\item spin down, remove residual wash, let pellet air-dry (a few minutes)
	\item label new set of tubes.
	\item add $25\mu l$ NFW, resuspend pellet, incubate 2min
	\item transfer eluate to fresh tube.
	\item use $1\mu l$ for qubit. (aim 15ng/$\mu l$, 10 more typical)
\end{itemize}
{\bf Pool samples to obtain $700ng/51\mu l$. If too dilute, additional bead clean up}.

\section*{Conditional: additional clean-up}
\begin{itemize}
	\item Pool sample to have at least 1200ng DNA in pool with even representation.
	\item Add the same volume of AmpXP beads
	\item mix and incubate 5min on rotator
	\item pellet on magnet, remove supernatant
	\item add $200\mu l$ of 70\% ethanol. keep on magnet, don't resuspend.
	\item remove ethanol, repeat ethanol wash.
	\item spin down, remove residual wash, let pellet air-dry (a few minutes)
	\item add $51\mu l$ NFW, resuspend pellet, incubate 2min
	\item transfer eluate to fresh tube.
	\item use $1\mu l$ for qubit. (needs to be at 15ng/$\mu l$, 20-30 more typical)
	\item dilute in fresh tube to obtain $700ng/51\mu l$
\end{itemize}


\section*{Adapter ligation}
{\bf we use a different ligase than in the ONT protocol}
\begin{itemize}
	\item add $20\mu l$ of BAM
	\item add $30\mu l$ Ultra II ligase master mix  (red cap)
	\item add $1\mu l$ Ultra II enhancer (red cap)
	\item mix thoroughly by gentle pipetting. Use P200
	\item RT for 10 min
\end{itemize}


\section*{ABB bead clean-up}
{\bf Note the odd bead volume, but it works...}
\begin{itemize}
	\item Add $40\mu l$ of AmpXP beads
	\item mix by pipetting and incubate 5min on rotator
	\item pellet on magnet, remove supernatant
	\item add $140\mu l$ of ABB. RESUSPEND by flicking (or gentle vortex).
	\item repeat
\end{itemize}

\section*{Recover library}
\begin{itemize}
	\item resuspend in $15\mu l$ ELB.
	\item Incubate 10min at RT
	\item (prepare the minION)
	\item pellet on magnet, remove supernatent into FRESH TUBE
	\item qubit with $1\mu l$ $~200ng$.
	\item store library on ice
\end{itemize}

\section*{Run Prep}
\begin{itemize}
	\item Prepare priming buffer (PB): 480 $\mu l$ RBF and 520 $\mu l$ NFW in Eppendorf 
	\item Prepare library for loading: Mix 35 $\mu l$ RBF + 25.5 $\mu l$ LLB (library loading beads) + 12 $\mu l$ of library + 2.5 $\mu l $ NFW in clean Eppendorf
	\item Prime flow cell: Open the sample port by swinging the gate open. Draw a trace amount of yellow fluid from region using the screw of P1000. Discard. Load 800 $\mu $ of PB.
	\item Wait 5 minutes
	\item Lift spot on port.
	\item Load remaining 200 $\mu l$ of PB
	\item Drop your library into the spot on port. DROP BY DROP WITHOUT TOUCHING
	\item Start sequencing. Log run statistics.
	\item Modify paths within Albacore scripts. Run basecalling.
\end{itemize}

\end{document}
